The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2013-07-25 main/s_background.tex
fix makefile; add section "Level 0" file; change wording on strictness

\end{itemize}
%
satisfying natural coherence conditions.
%
The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
Modulo the \emph{strictness} induced by the use of DeMorgan duality and one-sided sequents, e.g.\ $A=\dual*A$ rather than $A\cong\dual*A$, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
\MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.

>>>>

\end{itemize}
%
satisfying natural coherence conditions.
%
The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
The formulation used induces various forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, one-sided sequents mean the closure adjunction is an equivalence of categories, and the associativities are identities by decree.
%
Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.
